### 2019-02-21 sections/relatedwork.tex
more references

HipHop \cite{berry2011hiphop} is a programming language tailored to the development synchronous reactive web systems.
From a single source, both server and client applications can be generated.
Programs are written in the Hop language, a Scheme dialect.
Communication is based on a reactive layer embedded in Hop.
The set of HipHop reactive statements is based on those of the Esterel language \cite{boussinot1991esterel}.
Each reactive component starts by specifying possible input and output events.
The component then proceeds as a state machine.

>>>>

HipHop \cite{berry2011hiphop,journals/corr/BerryS13} is a programming language tailored to the development synchronous reactive web systems.
From a single source, both server and client applications can be generated.
Programs are written in the Hop language, a Scheme dialect.
Communication is based on a reactive layer embedded in Hop.
The set of HipHop reactive statements is based on those of the Esterel language \cite{boussinot1991esterel,journals/scp/BerryG92}.
Each reactive component starts by specifying possible input and output events.
The component then proceeds as a state machine.
